## S3 objects

1. Following the cohort example in the notes, suppose we want to create a `mean` method.
2. List all S3 methods associated with the `mean` function.
```{r }
methods("mean")
```
3. Examine the source code of `mean`. 
```{r results="hide"}
body("mean")
```
4. What are the arguments of `mean`?
```{r }
args("mean")
```
5. Create a function called `mean.cohort` that returns a vector containing the mean weight and mean height. Ensure that you can pass in the standard `mean` arguments, i.e.`na.rm`.`
```{r results='hide'}
mean.cohort = function(x, ...) {
  m1 = mean(x$details[ ,1], ...)
  m2 = mean(x$details[ ,2], ...)
  return(c(m1, m2))
}
```
6. Let's now make a similar function for the standard deviation. Look at the arguments of the `sd` function.
7. Create an function call `sd.cohort` that returns a vector containing the weight and height standard deviation. Ensure that you can pass in the standard `sd` arguments, i.e.`na.rm`.`
8. Create a default `sd` function. Look at `cor.default` in the notes for a hint.
```{r }
sd = function(x, ...) UseMethod("sd")
sd.default = function(x, ...) stats::sd(x, ...)
sd.cohort = function(x, ...) {
  s1 = sd(x$details[ ,1], ...)
  s2 = sd(x$details[ ,2], ...)
  return(c(s1, s2))
} 
```
9. Create a `summary` method for the `cohort` class. When the `summary` function is called on a `cohort` object it should call the base `summary` on the `details` 
element.
10. Use the `body` function to check if the function is already a generic function.
11. Use the `args` function to determine the arguments.
12. Create a `summary.cohort` function
```{r }
## summary is already a generic
body(summary)

## Match the args
args(summary)

## Function
summary.cohort = function(object, ...) summary(object$details, ...)
```
13. Create a `hist` method for the `cohort` class. When the `hist` function is called on a `cohort` object, it should produce a single plot showing two histograms - one for height and another for weight. You can either use base or **ggplot2**, again we'll be using **ggplot2**. To get both plots onto one plotting window, try using the `grid.arrange()` function from **gridExtra** package.
```{r }
## hist is already a generic
body(hist)

## Match the args
args(hist)

## Function
hist.cohort = function(x, ...) {
  dd = x$details
  Weight = ggplot(dd, aes(x = weight)) + 
    geom_histogram() + 
    labs(title = "Weight")
  Height = ggplot(dd, aes(x = height)) + 
      geom_histogram() + 
      labs(title = "Height")
  gridExtra::grid.arrange(Weight, Height)
}
```
14. Create a `[` method for the `cohort` class. This method should return a `cohort` object, but with the relevant rows sub setted. For example, if `cc` was a cohort object, then
```{r, eval=FALSE, echo = TRUE}
cc[1:3,]
```
\noindent would return the first three rows of the data frame.
```{r }
## Lots of methods available. 
methods('[')

## Examine [.data.frame
args('[.data.frame')

'[.cohort' = function(x, ...){
  x$details = x$details[...]
  x
}
```
15. Create a `[<-` method for the `cohort` class. This method should allow us to replace values in the `details` data frame, i.e.
```{r, eval=FALSE, echo = TRUE}
cc[1,1] = 10
```
```{r , eval = FALSE}
## Lots of methods available. 
methods('[<-')

## Examine [.data.frame
args('[<-.data.frame')

'[<-.cohort' = function(x, i, j, value){
  x$details[i, j] = value
  x
}
cc[1:3, ] = 55
```


## Solutions

Solutions are contained within the course package
```{r, eval=FALSE, echo = TRUE}
library("jrOOP")
vignette("solutions2", package="jrOOP")
```
